SPARQL on the Open, Decentralised Web

### 2016-07-30 dissertation/acknowledgments.tex
another ack

The Perl community have also been important in developing the ideas
and the code of this thesis. In addition to Gregory Todd Williams, I
would like to thank Toby Inkster, Chris Prather, Kip Hampton, Robin
Berjon, Michael Nachbaur and Jonas Smedegaard.

>>>>

The Perl community have also been important in developing the ideas
and the code of this thesis. In addition to Gregory Todd Williams, I
would like to thank Toby Inkster, Chris Prather, Kip Hampton, Robin
Berjon, Shawn M.  Moore, Michael Nachbaur and Jonas Smedegaard.
